
# Reading the data from the provided link & storing it in a variable

```{r}
dataset <- read.csv("http://bit.ly/w-data")
```

# Plotting the data to check if hours & scores are linearly related

```{r}
plot(dataset$Hours,dataset$Scores,xlab = "Hours Studied",ylab = "Percentage Score",
     main = "Hours vs Percentage")
```

# Since the scatterplot is linear, we can use linear regression to predict the scores

# splitting the data into training set and test set

```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$Scores, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```

# Fitting Simple Linear Regression to the Training set

```{r}
regressor = lm(formula = Scores ~ Hours,
               data = training_set)
```

# Predicting the Test set results

```{r}
y_pred = predict(regressor, newdata = test_set)
```

# Visualising the Training set results

```{r}
library(ggplot2)
ggplot() +
  geom_point(aes(x = training_set$Hours, y = training_set$Scores),
             colour = 'red') +
  geom_line(aes(x = training_set$Hours, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Score vs Hours (Training set)') +
  xlab('Hours Studied') +
  ylab('Percentage Score')
```

# Visualising the Test set results

```{r}
library(ggplot2)
ggplot() +
  geom_point(aes(x = test_set$Hours, y = test_set$Scores),
             colour = 'red') +
  geom_line(aes(x = training_set$Hours, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Score vs Hours (Test set)') +
  xlab('Hours Studied') +
  ylab('Percentage Score')
```

# Predicting the score for 9.25 hours spent (question)

```{r}
newset <- data.frame("Hours"=9.25,"Scores"=0)
own_score_prediction <- predict(regressor,newdata = newset)
newset <- data.frame("Hours"=9.25,"Scores"=own_score_prediction)
print(newset)
```

# Plotting the predicted result against the regression line

```{r}
ggplot() +
  geom_point(aes(x = training_set$Hours, y = training_set$Scores),
             colour = 'black') +
  geom_point(aes(x = test_set$Hours, y = test_set$Scores),
             colour = 'blue') +
  geom_point(aes(x = newset$Hours, y = newset$Scores),
             colour = 'red',size=7) +
  geom_line(aes(x = training_set$Hours, y = predict(regressor, newdata = training_set)),
            colour = 'blue') +
  ggtitle('Score vs Hours (Test set)') +
  xlab('Hours Studied') +
  ylab('Percentage Score')
```

